Incorporating Gyroscope Information in Gesture Recognition

### 2011-12-17 paper/paper.tex
fixed data

\begin{center}
\begin{tabular}{ | l | l | l | l | l | }
  \hline
  Normalization & Features & Gestures Types & Accuracy \\ \hline
  Yes	&	Both  &	All &	94.6\% \\ \hline
  Yes	&	Both	&	All &	89.6\% \\ \hline
  Yes	&	Accel &	All &	92.0\% \\ \hline
  Yes	&	Accel &	All &	84.2\% \\ \hline
  Yes	&	Gyro  &	All &	92.3\% \\ \hline
  Yes	&	Gyro  &	All &	89.7\% \\ \hline
  Yes	&	Both	&	All &	96.7\% \\ \hline
  Yes	&	Both	&	All &	97.9\% \\ \hline
  Yes	&	Both  &	All &	98.4\% \\ \hline
  No	&	Both	&	All &	98.4\% \\ \hline
  Yes	&	Both	& Squares &	100\% \\ \hline
  Yes	&	Both	& Circles and Reversed-circles  &	Chance \\ \hline
  Yes	&	Both	& Circles and Reversed-circles  &	72.0\% \\ \hline
  Yes	&	Both  & Circles and Reversed-circles  &	88.8\% \\
  \hline
\end{tabular}
\end{center}

>>>>

\begin{center}
\begin{tabular}{ | l | l | l | l | l | }
  \hline
  Normalization & Features & Algorithm & Gestures Types & Accuracy \\ \hline
  Yes	&	Both  &	All & Cluster-matching with HMM &	94.6\% \\ \hline
  Yes	&	Both	&	All & Original  &	89.6\% \\ \hline
  Yes	&	Accel &	All & Cluster-matching with HMM &	92.0\% \\ \hline
  Yes	&	Accel &	All &	Original & 84.2\% \\ \hline
  Yes	&	Gyro  &	All & Cluster-matching with HMM & 92.3\% \\ \hline
  Yes	&	Gyro  &	All & Original &  89.7\% \\ \hline
  Yes	&	Both	&	All &	Cluster-matching &  96.7\% \\ \hline
  Yes	&	Both	&	All &	Cluster-matching &  97.9\% \\ \hline
  Yes	&	Both  &	All &	Cluster-matching & 	98.4\% \\ \hline
  No	&	Both	&	All &	Cluster-matching & 	98.4\% \\ \hline
  Yes	&	Both	& Squares &	Cluster-matching & 	100\% \\ \hline
  Yes	&	Both	& Circles and Reversed-circles  &	Cluster-matching & 	Chance \\ \hline
  Yes	&	Both	& Circles and Reversed-circles  &	Cluster-matching with HMM &	72.0\% \\ \hline
  Yes	&	Both  & Circles and Reversed-circles  &	Cluster-matching with HMM	& 88.8\% \\
  \hline
\end{tabular}
\end{center}
